Computer Science House Constitution

### 2024-04-07 constitution.tex
Clarify Resignation of Chair (#57)
* Rebase off of current master branch

* Generalize process

---------

Co-authored-by: Sam Cordry <samcordry@gmail.com>
Co-authored-by: Ella Soccoli <112343747+esoccoli@users.noreply.github.com>

\asection{Executive Board Resignations}
An E-Board Member may resign from their E-Board position by submitting in writing the reason for resignation to the Chair.
The E-Board resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new director, as described in section \ref{Appointment of an Interim Director}, will begin at that time.
Following a resignation, the selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.

>>>>

\asection{Executive Board Resignations}
An E-Board Member may resign their position by submitting in writing the reason for resignation to the Chair.
The E-Board resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new director, as described in section \ref{Appointment of an Interim Director}, will begin at that time.
Following a resignation, the selection process, as defined in \ref{Selection}, of a replacement for the position vacated must begin within two weeks from when the resignation took place.
To postpone such a selection, the Chair may chair an Immediate Relative Majority Vote during a House Meeting prior to the beginning of the selection process to delay the selection process by a specified amount of time.

\asection{Selection of an Acting Chairperson}
If there is not an acting Chair during a process where one is required, then the following line of succession is used to determine which director becomes the acting Chair until a new Chair is elected.
\begin{enumerate}
	\item[1.] Evals Director
	\item[2.] Financials Director
	\item[3.] Voting E-Board Member chosen by an E-Board Vote
\end{enumerate}
